Fluoroproj: Title to be decided later

### 2023-10-20 manuscript/manuscript.qmd
manuscript updates

There was a temporal disconnect between some of the fluorometric analysis and the phytoplankton collection dates. All phytoplankton samples were collected on 2021-10-06. Samples from Barber, Indian and Yawgoo were collected on 2021-10-06 and samples from Curran, Mashapaug, and Warwick were collected on 2021-10-22; fluoromery was performed with 24 hours of sample collection.

@@

Don't read anything into absolute values (i.e. chlorophyll from one sensor not equal to chlorophyll from another sensor) across sensors, but general patterns are still very useful

@@

>>>>

All phytoplankton samples were collected on 2021-10-06. Samples from Barber, Indian and Yawgoo were collected on 2021-10-06 and samples from Curran, Mashapaug, and Warwick were collected on 2021-10-22; fluoromery was performed with 24 hours of sample collection.

@@

Don't read anything into absolute values (i.e. chlorophyll from one sensor not equal to chlorophyll from another sensor) across sensors, but general patterns are still very useful. Need to know info about specific sites to be useful.

@@

Extracted chla and phyco good for cell counts. Outliers for instruments don't throw off either extracted measurements.
